The Effects of weather on maize yield: New evidence from Kenya

### 2019-01-15 writing/draft4/draft22.tex
working MAPE writing

\begin{center}
\begin{threeparttable}
\caption{\label{R2}Coefficient of determination $R^2$ for mixed models}
\begin{indented}
\item[]
\begin{tabular}{@{}lcc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&Marginal\tnote{a}&Conditional\tnote{b}\\
\hline
{All counties}& $0.300$&$0.526$\\
{ASAL}& $0.134$&$0.353$\\
{non-ASAL}&  $0.153$&$0.436$\\
\br
\end{tabular}
\begin{tablenotes}
\begin{footnotesize}
    \item \textit{Notes:} The coefficient of determination for generalised linear mixed-effects models \cite{Nakagawa2013}.  \\
        \begin{adjustwidth}{1cm}{}
    \item[a] The marginal $R^2$ is interpreted as the variance explained by the fixed effects
  \item[b] The conditional $R^2$ is explained by both fixed affects and random effects (in our case by fixed effects and random intercepts)
     \end{adjustwidth}
     \end{footnotesize}
\end{tablenotes}

\end{indented}
\end{threeparttable} 
\end{center}
\vspace{1cm}

@@

%\item Possibly estimate simple regressions with the same explanatory variables as the preferred mixed effects specification. This would give us an approximation of $R^2$ which could be used to compare our models.

\begin{center}
\begin{threeparttable}
\caption{\label{CVsc}Cross validation: Mean absolute prediction error divided by IQR}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&\textbf{All covariates}&\textbf{Only seasonal}&\textbf{Naive forecast}\\
\hline
{All counties}&$0.3811$&$0.3889$&$0.4277$\\
{ASAL}&$0.5300$&$0.5342$&$0.5835$\\
{non-ASAL}&$0.3858$&$0.4043$&$0.4510$\\
\br
\end{tabular}
\end{indented}
\end{threeparttable} 
\end{center}
\vspace{1cm}

@@

\begin{center}
\begin{threeparttable}
\caption{\label{CV}Cross validation: Mean absolute prediction error}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&\textbf{All covariates}&\textbf{Only seasonal}&\textbf{Naive forecast}\\
\hline
{All counties}&$0.3599$&$0.3673$&$0.4040$\\
{ASAL}&$0.4352$&$0.4385$&$0.4790$\\
{non-ASAL}&$0.2715$&$0.2845$&$0.3173$\\
\br
\end{tabular}
\end{indented}
\end{threeparttable} 
\end{center}
\vspace{1cm}

@@

>>>>

\begin{center}
\begin{threeparttable}
\caption{\label{R2}Coefficient of determination $R^2$ for mixed models}
\begin{indented}
\item[]
\begin{tabular}{@{}lcc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&Marginal\tnote{a}&Conditional\tnote{b}\\
\hline
{All counties}& $0.300$&$0.526$\\
{ASAL}& $0.134$&$0.353$\\
{non-ASAL}&  $0.153$&$0.436$\\
\br
\end{tabular}
\begin{tablenotes}
\begin{footnotesize}
    \item \textit{Notes:} The coefficient of determination for generalised linear mixed-effects models \cite{Nakagawa2013}.  \\
        \begin{adjustwidth}{1cm}{}
    \item[a] The marginal $R^2$ is interpreted as the variance explained by the fixed effects
  \item[b] The conditional $R^2$ is explained by both fixed affects and random effects (in our case by fixed effects and random intercepts)
     \end{adjustwidth}
     \end{footnotesize}
\end{tablenotes}     
\end{indented}
\end{threeparttable} 
\end{center}
\vspace{1cm}

@@

To evaluate out of sample prediction accuracy of our models we implemented a procedure which is sometimes called the \textit{jackknife}. We re-estimated the preferred mixed effects models $n$-times, where $n$ is the number of observations (in our case $1300$ for the sample of all counties and $698$ and $602$ for the subsamples of ASAL and non-ASAL counties, respectively), each time we left out one observation. We subsequently used each of these $n$ estimated models to generate a predicted value 
of log of maize yield of the left-out observation. Then we calculated the absolute value of the difference between the predicted and real value of the left-out observation for each of the $n$ models. In the next step, we averaged the $n$ absolute values of the differences between predicted and real values to obtain the mean absolute prediction error (MAPE). Finally, we scaled the MAPE values by dividing them by the interquartile range (IQR) of the sample obtained as a difference between the third and first quartiles.

Besides obtaining the MAPE of our preferred specifications, we calculated MAPE of baseline models specified as mixed effects models with the set of fixed effects including two measures, in particular cumulative seasonal precipitation and seasonal average temperature. The only random effects of the baseline models are random intercepts as in our preferred specification and the baseline models have the same error structure ARMA($1$,$1$) as our main models. For the sake of comparison, we further calculated MAPE of naive forecasts defined as the last period's actual values of each county.

\begin{center}
\begin{threeparttable}
\caption{\label{CV}	Leave-one-out cross validation: Mean absolute prediction error divided by IQR}
\linespread{1.3}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&\textbf{All covariates\tnote{a}}&\textbf{Only seasonal\tnote{b}}&\textbf{Naive forecast\tnote{c}}\\
\hline
{All counties}&$0.3811$&$0.3889$&$0.4277$\\
{ASAL}&$0.5300$&$0.5342$&$0.5835$\\
{non-ASAL}&$0.3858$&$0.4043$&$0.4510$\\
\br
\end{tabular}
\end{indented}
 \begin{tablenotes}
  \begin{footnotesize}
  \item[a] Mixed effects models: the preferred specification with all fixed effects presented in table~\ref{MainEst}.
  \item[b] Mixed effects models: the baseline specification, only seasonal precipitation and average seasonal temperature in the fixed effects.
  \item[c] Last period's actual values used as this period's forecast.
  \end{footnotesize}
\end{tablenotes}
\end{threeparttable} 
\end{center}
\vspace{1cm}

@@

\begin{center}
\begin{threeparttable}
\caption{\label{CV}	Leave-one-out cross validation: Mean absolute prediction error}
\linespread{1.3}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&\textbf{All covariates\tnote{a}}&\textbf{Only seasonal\tnote{b}}&\textbf{Naive forecast\tnote{c}}\\
\hline
{All counties}&$0.3599$&$0.3673$&$0.4040$\\
{ASAL}&$0.4352$&$0.4385$&$0.4790$\\
{non-ASAL}&$0.2715$&$0.2845$&$0.3173$\\
\br
\end{tabular}
\end{indented}

 \begin{tablenotes}
  \begin{footnotesize}
  \item[a] Mixed effects models: the preferred specification with all fixed effects presented in table~\ref{MainEst}.
  \item[b] Mixed effects models: the baseline specification, only seasonal precipitation and average seasonal temperature in the fixed effects.
  \item[c] Last period's actual values used as this period's forecast.
  \end{footnotesize}
\end{tablenotes}
\end{threeparttable} 
\end{center}
\vspace{1cm}

@@

\doublespacing
